The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-14 talk/vmil2012/paper.tex
get rid of the strangeish full stops at the end of non-sentences

%Section~\ref{sec:Evaluation} presents Figures about the absolute number of
%operations for each benchmark, and the overhead produced by the information
%stored at the different levels for the guards
In this paper we want to substantiate the aforementioned observations and
describe based on them the reasoning behind the implementation of guards in
RPython's tracing just-in-time compiler. the contributions of this paper are:
\begin{itemize}
  \item An analysis and benchmark of guards in the context of RPython's tracing JIT.
  %An analysis of guards in the context of RPython's tracing JIT to
  %substantiate the aforementioned observation, based on a set of benchmarks,
  \item detailed measurements about the frequency and the
  overhead associated with guards, and
  \item a description about how guards are implemented in the high\-
  and low-level components of the JIT and describe the rationale behind the design.
\end{itemize}

>>>>

%Section~\ref{sec:Evaluation} presents Figures about the absolute number of
%operations for each benchmark, and the overhead produced by the information
%stored at the different levels for the guards
In this paper we want to substantiate the aforementioned observations and
describe based on them the reasoning behind the implementation of guards in
RPython's tracing just-in-time compiler. The contributions of this paper are:
\begin{itemize}
  \item An analysis and benchmark of guards in the context of RPython's tracing JIT,
  %An analysis of guards in the context of RPython's tracing JIT to
  %substantiate the aforementioned observation, based on a set of benchmarks,
  \item detailed measurements about the frequency and the
  overhead associated with guards, and
  \item a description about how guards are implemented in the high\-
  and low-level components of the JIT and a description of the rationale behind the design.
\end{itemize}
